`methyvim`: Targeted and Model-free Differential Methylation Analysis in

### 2017-10-19 README.Rmd
minor name updates

> Targeted learning of variable importance measures for the analysis of
> differential methylation experiments

@@

        @article{hejazi2017methyvim,
          doi = {},
          url = {},
          year  = {2017},
          month = {},
          publisher = {},
          volume = {},
          author = {Hejazi, Nima S and Hubbard, Alan E and {van der Laan}, Mark
            J},
          title = {methyvim: Targeted and model-free analysis of differential
            methylation in R},
          journal = {}
        }

>>>>

> Targeted Data-Adaptive Estimation and Inference for Differential Methylation
> Analysis

@@

        @article{hejazi2017methyvim,
          doi = {},
          url = {},
          year  = {2017},
          month = {},
          publisher = {},
          volume = {},
          author = {Hejazi, Nima S and Hubbard, Alan E and {van der Laan}, Mark
            J},
          title = {methyvim: Targeted and model-free differential methylation
            analysis in R},
          journal = {}
        }

### 2017-10-19 paper/paper_BiocF1000.Rmd
minor name updates

---
title: '`methyvim`: Targeted and Model-free Analysis of Differential Methylation
in R'
author:
  - name: Nima S. Hejazi
    affiliation: Division of Biostatistics, University of California, Berkeley
    orcid: 0000-0002-7127-2789
  - name: Rachael V. Phillips
    affiliation: Division of Biostatistics, University of California, Berkeley
    orcid: 0000-0002-8474-591X
  - name: Alan E. Hubbard
    affiliation: Division of Biostatistics, University of California, Berkeley
    orcid: 0000-0002-3769-0127
  - name: Mark J. van der Laan
    affiliation: Division of Biostatistics, University of California, Berkeley
    orcid: TBA
abstract: |
  We present `methyvim`, a general algorithm for the nonparametric estimation of
  treatment/exposure effects on DNA methylation at CpG sites, complete with
  straightforward statistical inference for such estimates. This approach
  leverages variable importance measures, a class of parameters that arise in
  causal inference and are defined in such a manner that they provide targeted
  estimates of the relative importance of individual CpG site with respect to
  a binary exposure/treatment assigned at the level of subjects. Additionally,
  this procedure is computationally efficient; incorporating a preliminary
  screening step to isolate a subset of sites for which there is cursory
  evidence of differential methylation and a multiple testing correction step
  to control the False Discovery Rate as if all sites were tested. This
  technique for analysis of differentially methylated positions provides an
  avenue to move beyond linear models without the loss of interpretable
  statistical inference.
keywords: DNA methylation, differential methylation, epigenetics, causal
  inference, statistical variable importance, targeted minimum loss-based
  estimation, machine learning
bibliography: paper_BiocF1000.bib
output: BiocWorkflowTools::f1000_article
---

@@

We refer the reader to the package vignette, "`methyvim`: Targeted Learning for
Differential Methylation Analysis," included in any distribution of the software
package, for further details.

>>>>

---
title: '`methyvim`: Targeted and Model-free Differential Methylation Analysis in
  R'
author:
  - name: Nima S. Hejazi
    affiliation: Division of Biostatistics, University of California, Berkeley
    orcid: 0000-0002-7127-2789
  - name: Rachael V. Phillips
    affiliation: Division of Biostatistics, University of California, Berkeley
    orcid: 0000-0002-8474-591X
  - name: Alan E. Hubbard
    affiliation: Division of Biostatistics, University of California, Berkeley
    orcid: 0000-0002-3769-0127
  - name: Mark J. van der Laan
    affiliation: Division of Biostatistics, University of California, Berkeley
    orcid: TBA
abstract: |
  We present `methyvim`, a general algorithm for the nonparametric estimation of
  treatment/exposure effects on DNA methylation at CpG sites, complete with
  straightforward statistical inference for such estimates. This approach
  leverages variable importance measures, a class of parameters that arise in
  causal inference and are defined in such a manner that they provide targeted
  estimates of the relative importance of individual CpG site with respect to
  a binary exposure/treatment assigned at the level of subjects. Additionally,
  this procedure is computationally efficient; incorporating a preliminary
  screening step to isolate a subset of sites for which there is cursory
  evidence of differential methylation and a multiple testing correction step
  to control the False Discovery Rate as if all sites were tested. This
  technique for analysis of differentially methylated positions provides an
  avenue to move beyond linear models without the loss of interpretable
  statistical inference.
keywords: DNA methylation, differential methylation, epigenetics, causal
  inference, statistical variable importance, targeted minimum loss-based
  estimation, machine learning
bibliography: paper_BiocF1000.bib
output: BiocWorkflowTools::f1000_article
---

@@

We refer the reader to the package vignette, "`methyvim`: Targeted Data-Adaptive
Estimation and Inference for Differential Methylation Analysis," included in any
distribution of the software package, for further details.
